Polynomial Chaos for the Estimation of Manning's Friction

### 2013-12-16 paper/pcstudy.tex
revisiting results section

Figure~\ref{fig:rlzs} shows the evolution of the
water surface elevation for the 125 realizations obtained 
to compute the PC expansions at the four different gauge 
locations. We notice that the variation in surface elevation 
is negligible during the first hour at gauge number 21418 
and during the first two hours for the remaining gauges
as the plots of the different realizations are seen to superimpose.
However, a noticeable uncertainty in the surface 
elevation can be seen  at all gauges as indicated from the thickness 
of the bands formed by the plots of the realizations. This uncertainty
occurs till the end of the simulations.

In order to check the consistency of the approximation, we compare
 water surface elevation from the realizations 
with those obtained from the PC surrogate. The different curves
show an excellent agreement (not shown) for all times. We also define
an error metric that measures the relative normalized root mean-square error between the left hand side function 
in Equation~(\ref{eq:stochseries})
and its PC representation at the sampling points:
\begin{equation} 
   E = \frac{\displaystyle
         \left(\sum_{\xxi \in \NISP} \left|U(\xxi) - \sum_{k = 0}^{P}
U_k\Psi_k(\xxi)\right|^2
         \right)^{1/2}}
        {\displaystyle
          \left(\sum_{\xxi \in \NISP} \left|U(\xxi)\right|^2\right)^{1/2} 
          },
\label{eq:error}
\end{equation}
where $\NISP$ is the 125-member ensemble obtained using the PC algorithm. 
This error metric calculated at the different gauge locations is shown in Figure~\ref{fig:error};
the largest relative normalized error for 
water surface elevation is about 0.1\%.

>>>>

Figure~\ref{fig:rlzs} shows the evolution of the
water surface elevation predicted at the four different gauges 
using \geoclaw for the 125 different realizations 
required to compute the PC expansions. We notice that the 
variability in water surface elevation is insignificant for the first 
hour at all gauges as the plots of the different realizations superimpose.
Later, the variability starts to increase with time at the different gauges 
as indicated from the thickness of the bands formed by the plots of the realizations
and is significant at $t\sim$ 5400~s, 6000~s, 3600~s and 7200~s
for gauges 21401, 21413, 21418, 21419 respectively.
This is consistent with the distance from the gauge to the source of the earthquake
where gauge 21418 is the closest and gauge 21419 is the farthest.
The uncertainty in the water surface  elevation continues till the end of the simulations
at all gauges.

In order to check the consistency of the PC approximation, we compare
water surface elevation from the realizations 
with those obtained from the PC surrogate. The different curves
show an excellent agreement (not shown) for all times and gauges locations.
To quantify this agreement, we define
an error metric that measures the relative normalized root mean-square error between the left hand side function 
in Equation~(\ref{eq:stochseries}) and its PC representation at the sampling points:

\begin{equation} 
   E = \frac{\displaystyle
         \left(\sum_{\xxi \in \NISP} \left|U(\xxi) - \sum_{k = 0}^{P}
U_k\Psi_k(\xxi)\right|^2
         \right)^{1/2}}
        {\displaystyle
          \left(\sum_{\xxi \in \NISP} \left|U(\xxi)\right|^2\right)^{1/2} 
          },
\label{eq:error}
\end{equation}
where $\NISP$ is the 125-member ensemble obtained using the PC algorithm. 
This error metric calculated at the different gauge locations is shown in Figure~\ref{fig:error};
the largest relative normalized error for 
water surface elevation is about 0.1\%.

### 2013-12-16 paper/results.tex
revisiting results section

\section{Results}
\label{sec:results}
We begin the results section by performing
an error and convergence analysis of the
constructed surrogate using the PC expansions
to establish its validity in Section~\ref{sec:analysis}.
Then in Section~\ref{sec:forward}, we present
statistical analysis to quantify the uncertainty in the predicted surface elevation
as well as a sensitivity analysis to rank the impact of the different Manning's 
roughness coefficients on this uncertainty. 
Finally, in Section~\ref{sec:inverse}, we present the results of the inverse
problem where we determined the posterior distributions of the input parameters 
and analyzed them in light of the available gauge data.
\input{pcstudy}
\input{analysis}
\input{mcmc}

>>>>

\section{Results}
\label{sec:results}
We begin the results section by performing an error and convergence 
analysis of the constructed surrogate using the PC expansions to 
establish its validity in Section~\ref{sec:analysis}.  In Section
~\ref{sec:forward}, we present a statistical analysis to quantify the 
uncertainty in the predicted water surface elevation in addition to a 
sensitivity analysis that enables us to rank the impact of the 
different Manning's roughness coefficients on the uncertainty. Finally, 
in Section~\ref{sec:inverse}, we present the results of the inverse problem 
where we determine the posterior distributions of the input uncertain
parameters and analyze them in light of the available gauge data.
\input{pcstudy}
\input{analysis}
\input{mcmc}
